\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage{tabularx}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabularx}{0.97\textwidth}[t]{X r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabularx}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape FIRST LAST} \\ \vspace{1pt}
    \small PHONE NUMBER $|$ \href{mailto:suri312006@gmail.com}{\underline{EMAIL}} $|$ 
    \href{https://www.linkedin.com/in/surendra-jammishetti-909809293/}{\underline{LINKED IN}} $|$
    \href{https://suridev.vercel.app/}{\underline{Personal Website}} $|$
    \href{https://github.com/suri312006}{\underline{github.com/suri312006}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Santa Cruz}{\textbf{GPA 3.97}}
      {Bachelor of Science in Computer Engineering}{Aug. 2023 -- Dec. 2025}
    % \resumeSubheading
    %   {Blinn College}{Bryan, TX}
    %   {Associate's in Liberal Arts}{Aug. 2014 -- May 2018}
    \resumeSubheading
    {Relevant Coursework}{}{ 
Data Structures and Algorithms, Computer Systems and C Programming, Logic Design with Verilog, Discrete Math, Linear Algebra} \\
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart


    \resumeSubheading
      {Lead Software Engineer}{March 2024 -- Present}
      {\href{ConnectifyAI}\underline{ConnectifyAI} $|$ \emph{Go, Python, Typescript, PostgreSQL, Docker}}{Santa Cruz, CA}
      \resumeItemListStart
        \resumeItem{Leading a team of \textbf{10} Undergrads and masters students, making important decisions such as deciding the tech stack, and managing the GitLab Repository.}
        \resumeItem{Utilizing Go and PostgreSQL to create a performant REST API for our services}
        \resumeItem{Learned Docker and GitLab Runner to automate backend deployments.}
        \resumeItem{Working with Professor Marinescu to research viable, performant methods to chain multiple AI/ML models.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Software Engineering Intern}{June 2024 -- Aug. 2024}
      {LightLinks $|$ \emph{Embedded Rust and C Programming, eBPF, XDP, Kernel Programming, Networking}}{Santa Cruz, CA}
      \resumeItemListStart
        \resumeItem{Engineered a Multi-Device system to facilitate a light-based network protocol.}
        \resumeItem{Utilized existing kernel frameworks, such as eBPF and XDP to implement project specifications.}
        \resumeItem{Lead the charge in migrating legacy C codebase to Rust for improved developer experience and reliability.}
        \resumeItem{Set up custom GitHub Actions runner to facilitate the building and testing of embedded networking software.}

        \resumeItemListEnd

    \resumeSubheading
    {Artificial Intelligence Researcher}{ Nov. 2023 -- Mar. 2024}
    {ACM AI Research Lab $|$ \emph{PyTorch, RAG, Kubernetes, Hugging Face}}{Santa Cruz, CA}
    \resumeItemListStart
    \resumeItem{Created a performance analysis pipeline to quantify the effectiveness of using different latent spaces to find similarities between code and English}
    \resumeItem{Took the lead in finding a problem space for a group of 5 people to investigate.}
    \resumeItem{Developed a rudimentary RAG to ascertain the quality of responses with different model architectures.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
      %replace this with term2term
          {\textbf{Term2Term} $|$ \emph{Rust, Go, gRPC, PostgreSQL, Docker, Github Actions}}{June 2024 -- Present}
          \resumeItemListStart
            \resumeItem{Programming a Rust TUI client capable of sending encrypted messages to other users.}
            \resumeItem{Developing a Go server to store encrypted messages in database and direct messages between users.}
            \resumeItem{Utilizing gRPC for performant type-safe communication across clients and server.}
            \resumeItem{Learning Peer-to-Peer communication to integrate into the client for complete user privacy.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{CoupledCats} $|$ \emph{Rust, gRPC, SQLite, Multithreading, GitHub Actions}}{August 2024 -- Present}
          \resumeItemListStart
            \resumeItem{Learning Bevy, a Rust game engine, to create a desktop application to connect clients with their significant others.}
            \resumeItem{Creating a strictly Peer-to-Peer platform for utmost privacy.}
            \resumeItem{Utilizing multithreading to run client / server processes along with the game engine event loop, using channels to facilitate communication.}
            % \resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Rust, Go, TypeScript / JavaScript, Python, C/C++, SQL (Postgres), HTML/CSS} \\
     \textbf{Frameworks}{: SvelteKit, Nuxt, Node.js, Django, Material-UI} \\
     \textbf{Developer Tools}{: Arch Linux, Nix, NeoVim, Git, Docker, Kubernetes, Vercel, PlanetScale, Google Cloud Platform, VS Code, IntelliJ} \\
     \textbf{Libraries}{: Tokio, Serde, React}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
